### 2015-06-22 paper/paper.tex
paper with the correct images

\begin{figure}[!t]
\begin{center}
\includegraphics[width=0.75\columnwidth]{figures/perez3}
\end{center}
\caption{$HV(P)$ of a given Pareto-front $P$}
\label{fig:hv}
\end{figure}

@@

\begin{figure}[!t]
\begin{center}
\includegraphics[width=1.0\columnwidth]{figures/perez6}
\end{center}
\caption{Optimal Pareto Front of the Deep Sea Treasure, with both objectives to be maximized.}
\label{fig:optDst}
\end{figure}

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{photos/perez.jpg}}]
{Diego Perez}
is currently pursuing a Ph.D. in Artificial Intelligence applied to games at the University of Essex (UK). He has published in the domain of Game AI, with research interests on Reinforcement Learning and Evolutionary Computation. He has organized several Game AI competitions, as the Physical Travelling Salesman Problem and the General Video Game AI competitions, both held in IEEE conferences. He also has programming experience in the videogames industry with titles published for game consoles and PC.
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{photos/sanaz.jpg}}]
{Sanaz Mostaghim} is a full professor of computer science at the Otto von Guericke University Magdeburg, Germany. She holds a PhD degree (2004) in electrical engineering and computer science from the University of Paderborn, Germany. She worked as a postdoctoral fellow at ETH Zurich in Switzerland and as a lecturer at Karlsruhe Institute of technology (KIT), Germany. Her research interests are in the area of swarm intelligence, evolutionary multi-objective optimisation and their applications in robotics, science and industry. She is an active member in several German and international societies such as IEEE and GI. She serves as an associate editor for IEEE Transactions on evolutionary computation and IEEE Transactions on cybernetics.
\end{IEEEbiography}

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{photos/lucas.png}}]{Simon Lucas}
(SMIEEE) is a professor of Computer Science at the University of Essex (UK) where he leads the Game Intelligence Group. His main research interests are games, evolutionary computation, and machine learning, and he has published widely in these fields with over 160 peer-reviewed papers. He is the inventor of the scanning n-tuple classifier, and is the founding Editor-in-Chief of the IEEE Transactions on Computational Intelligence and AI in Games.
\end{IEEEbiography}

>>>>

\begin{figure}[!t]
\begin{center}
\includegraphics[width=0.75\columnwidth]{figures/perez3b}
\end{center}
\caption{$HV(P)$ of a given Pareto-front $P$}
\label{fig:hv}
\end{figure}

@@

\begin{figure}[!t]
\begin{center}
\includegraphics[width=1.0\columnwidth]{figures/perez6b}
\end{center}
\caption{Optimal Pareto Front of the Deep Sea Treasure, with both objectives to be maximized.}
\label{fig:optDst}
\end{figure}

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{photos/perez.jpg}}]
{Diego Perez} is a Senior Research Officer at the University of Essex (UK). He holds a PhD degree (2015) in Computer Science and Electronic Engineering at the University of Essex. He has published in the domain of Game AI, with research interests on Reinforcement Learning and Evolutionary Computation. He has organized several Game AI competitions, as the Physical Travelling Salesman Problem and the General Video Game AI competitions, both held in IEEE conferences. He has programming experience in the videogames industry with titles published for game consoles and PC.
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{photos/sanaz.jpg}}]
{Sanaz Mostaghim} is a full professor of computer science at the Otto von Guericke University Magdeburg, Germany. She holds a PhD degree (2004) in Electrical Engineering and Computer Science from the University of Paderborn, Germany. She worked as a postdoctoral fellow at ETH Zurich in Switzerland and as a lecturer at Karlsruhe Institute of technology (KIT), Germany. Her research interests are in the area of swarm intelligence, evolutionary multi-objective optimisation and their applications in robotics, science and industry. She is an active member in several German and international societies such as IEEE and GI. She serves as an associate editor for IEEE Transactions on evolutionary computation and IEEE Transactions on cybernetics.
\end{IEEEbiography}

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{photos/lucas.png}}]{Simon Lucas}
(SMIEEE) is a professor of Computer Science at the University of Essex (UK) where he is the Head of School and leads the Game Intelligence Group. He holds a PhD degree (1991) in Electronics and Computer Science from the University of Southampton. His main research interests are games, evolutionary computation, and machine learning, and he has published widely in these fields with over 180 peer-reviewed papers. He is the inventor of the scanning n-tuple classifier, and is the founding Editor-in-Chief of the IEEE Transactions on Computational Intelligence and AI in Games.
\end{IEEEbiography}
